Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
Adaptive res text

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step. We compare the approximation made to accelerate
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

@@

\begin{table}
  \begin{center}
	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}

@@

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).}
  \label{fig:refine}
\end{figure}

@@

      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
        %l4
        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
        %l3
        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
        %l2
        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
        %l1
        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
        %l0
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          %ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
        %Hierarchical measurement
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
  With a regular grid, the curvature computation refines at every frame until it reaches the ground truth result.
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$)}
  \label{fig:timings}
\end{figure}

In this experiments, we measure the timings obtained when running our framework on a
GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
At each frame, both the curvature and the triangulation are recomputed.
If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
We measured those timings using the regular and the hierarchical algorithm. The results are presented
figure \ref{fig:timings}.

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

>>>>

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step. We compare the approximation made to accelerate 
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}.

@@

For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

\begin{table}
  \begin{center}

	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}

@@

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}

@@

      \begin{axis}[
          ybar stacked,
          ymode = log,
          ymax = 6000,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20,
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000) 
          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
        %l4
        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000) 
          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
        %l3
        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
        %l2
        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000) 
          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
        %l1
        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000) 
          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
        %l0
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000) 
          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}
	  \end{tikzpicture}
%
    \begin{tikzpicture}[scale=0.7]
      \begin{axis}[
          ybar stacked,
          ymax = 6000,
          ymode = log,
	  	  bar width=20pt,
	  	  nodes near coords,
	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
          enlargelimits=0.15,
          %ylabel={\#Time (in ms)},
          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20, 
	      Dragon-R8, Dragon-R20},
          xtick=data,
          point meta=rawy,
          x tick label style={rotate=45,anchor=east},
        ]
        %Geometry Generation
        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000) 
          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
        %Hierarchical measurement
        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000) 
          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
      \end{axis}

     \end{tikzpicture}
     \end{center}
  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (drak blue).
  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii (8, 10, 16, 20)}
  \label{fig:timings}
\end{figure}

In this experiments, we measure the timings obtained when running our framework on a
GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
At each frame, both the curvature and the triangulation are recomputed.
If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
We measured those timings using the regular and the hierarchical algorithm. The results are presented in 
logarithmic scale figure \ref{fig:timings}.

We can first note that the required time for an object to compute ground truth curvature is usually
as high as the time required to extract the geometry and compute all the above levels.
Using approximations is thus mandatory, since for big objects such as the XYZ Dragon (Digital Domain $510^3$)
with high radii, the computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds to compute, whereas
the approximated visualisation at $l_2$ takes only 300ms.
We can thus get an approximated visualisation of our object as soon as we run the application, allowing for
real time interactions with the object (changing the visualised value, the curvature radius, etc ...).
Once an interesting portion if the object is reached, it only takes a few seconds to the application to display
ground truth curvature estimation.

It is also clear on those graphs that using a hierarchical decomposition reduces the curvature computation time.
For the XYZ Dragon with a radius of 20, it needs almost 4 seconds to compute the $l_0$ level, whereas using the
hierarchical algorithm, it only needs 700ms. However, due to the precomputation, this algorithm is biased and
creates an error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}
